Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
fixing an acronym

The experiments were run in the same way as before, using several
Twitter announcements throughout several days by the end of July
2015. Eventually, more than one thousand experiments were completed in
a matter of days. A summary of results is shown in Table
\ref{tab:summary:ww}, comparing it with the aggregate of the results
obtained with the initial version of {\sf NodIO}. These results are
remarkably different, being similar only in the median and maximum
number of IPs, although in this case it would be combination
IP-worker, as we considered every worker as a unique IP. The median
number of seconds is almost 80\% better than the previous version, and
the median number of PUTs is three times better; this causes that most
of experiments take less time than one of the baselines, and one third
less than the second baseline. Thus, the conclusion in this case is
that we can obtain, through volunteer computation, a result that most of the times is better than we would by using a similar, non-parallel,
desktop setup, which makes this system suitable for massively
distributed evolutionary algorithms.
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value (GEV) and Weibull distribution of
  the number of {\tt PUT}s per worker. \label{tab:puts:ww}}
\begin{center}
\begin{tabular}{cccc}
\hline
Distribution & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
GEV & 18.275 $\pm$ 0.83719  &  25.962  $\pm$ 1.22015 & 1.242   $\pm$
0.04746 \\
Weibull & ND & 75.11457519 $\pm$ 2.97470251  & 0.69714410 $\pm$ 0.01383976 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%

@@

%
\begin{figure}[!htb]
\centering
\includegraphics{rastrigin-fitness.png}
\caption{Fitness of chromosomes sent to the server pool along time in
  the $x$ axis.} 
% Plotted with ../data/plot-rastrigin-fitness.R
\label{fig:puts:rastrigin}
\end{figure}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{rastrigin-IPs.png}
\includegraphics[width=0.49\linewidth]{rastrigin-IPs-hour.png}
\caption{Number of unique IPs participating in the Rastrigin
  experiment per minute (left) and per hour (right)} 
% Plotted with ../data/plot-rastrigin-IPs.R
\label{fig:ips:rastrigin}
\end{figure}
%
\begin{table*}
\caption{Summary of fit to Generalized Extreme Value (GEV) and Weibull distribution of
  the number of {\tt PUT}s per worker for the F15 (Rastrigin) function. \label{tab:puts:ww:f15}}
\begin{center}
\begin{tabular}{cccc}
\hline
Distribution & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
GEV & 35.759  &  343.336   & 9.877 \\
Weibull & ND & 29.002625061 $\pm$ 2.153034198  & 0.402393903 $\pm$ 0.007586468 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{gev-fit-ww-rastrigin-workers.png}
\includegraphics[width=0.49\linewidth]{weibull-fit-ww-rastrigin-workers.png}
\caption{Fit to GEV (left) and Weibull (right) of the number of {\tt PUT}s per worker for the F15 (Rastrigin) function.} 
% Plotted with ../data/ips-puts-rastrigin.R
\label{fig:fit:rastrigin}
\end{figure}
%

>>>>

The experiments were run in the same way as before, using several
Twitter announcements throughout several days by the end of July
2015. Eventually, more than one thousand experiments were completed in
a matter of days. A summary of results is shown in Table
\ref{tab:summary:ww}, comparing it with the aggregate of the results
obtained with the initial version of {\sf NodIO}. These results are
remarkably different, being similar only in the median and maximum
number of IPs, although in this case it would be combination
IP-worker, as we considered every worker as a unique IP. The median
number of seconds is almost 80\% better than the previous version, and
the median number of PUTs is three times better; this causes that most
of experiments take less time than one of the baselines, and one third
less than the second baseline. Thus, the conclusion in this case is
that we can obtain, through volunteer computation, a result that most of the times is better than we would by using a similar, non-parallel,
desktop setup, which makes this system suitable for massively
distributed evolutionary algorithms.
%
\begin{table*}
\caption{Summary of fit to GEV and Weibull distribution of
  the number of {\tt PUT}s per worker. \label{tab:puts:ww}}
\begin{center}
\begin{tabular}{cccc}
\hline
Distribution & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
GEV & 18.275 $\pm$ 0.83719  &  25.962  $\pm$ 1.22015 & 1.242   $\pm$
0.04746 \\
Weibull & ND & 75.11457519 $\pm$ 2.97470251  & 0.69714410 $\pm$ 0.01383976 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%

@@

%
\begin{figure}[!htb]
\centering
\includegraphics{rastrigin-fitness.png}
\caption{Fitness of chromosomes sent to the server pool along time in
  the $x$ axis.} 
% Plotted with ../data/plot-rastrigin-fitness.R
\label{fig:puts:rastrigin}
\end{figure}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{rastrigin-IPs.png}
\includegraphics[width=0.49\linewidth]{rastrigin-IPs-hour.png}
\caption{Number of unique IPs participating in the Rastrigin
  experiment per minute (left) and per hour (right)} 
% Plotted with ../data/plot-rastrigin-IPs.R
\label{fig:ips:rastrigin}
\end{figure}
%
\begin{table*}
\caption{Summary of fit to GEV and Weibull distribution of
  the number of {\tt PUT}s per worker for the F15 (Rastrigin) function. \label{tab:puts:ww:f15}}
\begin{center}
\begin{tabular}{cccc}
\hline
Distribution & Location $\mu$ & Scale $\sigma$ & Shape $\xi$ \\
\hline
GEV & 35.759  &  343.336   & 9.877 \\
Weibull & ND & 29.002625061 $\pm$ 2.153034198  & 0.402393903 $\pm$ 0.007586468 \\
\hline
\end{tabular}
\end{center}
\end{table*}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=0.49\linewidth]{gev-fit-ww-rastrigin-workers.png}
\includegraphics[width=0.49\linewidth]{weibull-fit-ww-rastrigin-workers.png}
\caption{Fit to GEV (left) and Weibull (right) of the number of {\tt PUT}s per worker for the F15 (Rastrigin) function.} 
% Plotted with ../data/ips-puts-rastrigin.R
\label{fig:fit:rastrigin}
\end{figure}
%
